---
title: "12_1"
author: "Adrian Goedeckemeyer"
date: "11/18/2016"
output: html_document
---

## 12.1

Work through the R Lab in the textbook, from pages 154-161. Then, using the “lalonde” data set in the “Matching” package, experiment with logistic regression by estimating propensity scores. After estimating propensity scores, try to estimate the linear predictor (transforming the propensity scores using the formula given in the text). Optional: attempt to simulate how changes in a feature (like re74) produce changes in the predicted (probability) value.

## ISLR Example

```{r}
library(ISLR)
names(Smarket)
dim(Smarket)
summary(Smarket)
pairs(Smarket)
cor(Smarket[,-9])
attach(Smarket)
plot(Volume)
glm.fit=glm(Direction ~ Lag1+Lag2+Lag3+Lag4+Lag5+Volume , data=Smarket ,family=binomial)
summary(glm.fit)
coef(glm.fit)

summary(glm.fit)$coef

glm.probs=predict(glm.fit,type="response")
glm.probs[1:10]

contrasts(Direction)

glm.pred=rep("Down",1250)
glm.pred[glm.probs >.5]="Up"

table(glm.pred,Direction)


(507+145) /1250
mean(glm.pred==Direction )

train=(Year <2005)
Smarket.2005= Smarket[! train ,]
dim(Smarket.2005)
Direction.2005=Direction[!train]

glm.fit=glm(Direction~Lag1+Lag2+Lag3+Lag4+Lag5+Volume , data=Smarket ,family=binomial,subset=train)
glm.probs=predict(glm.fit,Smarket.2005,type="response")

glm.pred=rep("Down",252)
glm.pred[glm.probs >.5]="Up"
table(glm.pred,Direction.2005)
mean(glm.pred==Direction.2005)
mean(glm.pred!=Direction.2005)

glm.fit=glm(Direction~Lag1+Lag2,data=Smarket ,family=binomial, subset=train)
glm.probs=predict(glm.fit,Smarket.2005,type="response")
glm.pred=rep("Down",252)
glm.pred[glm.probs >.5]="Up"
table(glm.pred,Direction.2005)

mean(glm.pred==Direction.2005)
106/(106+76)
predict(glm.fit,newdata=data.frame(Lag1=c(1.2,1.5), Lag2=c(1.1,-0.8)),type="response")
```

## Lalonde 

```{r}
library(Matching)
data(lalonde)
names(lalonde)
glm2.fit=glm(treat ~ age + educ + black + hisp + married + nodegr + re74 + re75 + u74 + u75 , data=lalonde ,family=binomial)
summary(glm2.fit)
coef(glm2.fit)

summary(glm.fit)$coef

```

$$p=\frac{ e^{1.622 + .00827*age - .221 * educ - .8557 * black + .196 * married - .8981 * nondegr - .00004466 * re74 + .00002924 * re75 - .1927 * u74 - .3369 * u75} }{ 1 + e^{1.622 + .00827*age - .221 * educ - .8557 * black + .196 * married - .8981 * nondegr - .00004466 * re74 + .00002924 * re75 - .1927 * u74 - .3369 * u75} }$$
