---
title: "Genetic Matching on Lalonde and DW"
author: "Adrian Goedeckemeyer"
date: "9/30/2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Assignment

### Comparing the two Datasets

Go to Rajeev Dehejia’s website (http://users.nber.org/\~rdehejia/nswdata2.html) and download the NSW data files labelled 
(i) Lalonde sample
(ii) Dehejia-Wahba sample

Calculate the difference in means of the outcome (re78) in both samples and run balance tests (t-tests) for key covariates. 

Are the estimated causal effects the same or similar? (Hint: they should not be the same, because the underlying treatment groups are very different.) 

Are the covariates well-balanced?

### Different Matching Algorithms on PSID and CPS Data

Now download the PSID and CPS data files and attempt to use Mahalanobis, propensity score, and genetic matching to reconstruct a matched data set in R (e.g., matchingnswre74_treated.txt), and you must use the “Match”, “GenMatch”, and “MatchBalance” functions—see the relevant help files. 

What are the properties of your matched data set? 

Are you able to recover the benchmark experimental estimate obtained in the randomized experiment?

```{r}
library(foreign)
lalonde = read.dta("~/Downloads/nsw.dta")
summary(lalonde)

dw = read.dta("~/Downloads/nsw_dw.dta")
summary(dw)
```
i) Difference in means:
```{r}
mean(lalonde$re78)-mean(dw$re78)
mean(lalonde$re78[lalonde$treat==1])-mean(dw$re78[dw$treat==1])
mean(lalonde$re78[lalonde$treat==0])-mean(dw$re78[dw$treat==0])
```

Compare a few t-tests for covariates:
```{r}
t.test(dw$re78, dw$married)
t.test(lalonde$re78, lalonde$married)

t.test(dw$re78, dw$education)
t.test(lalonde$re78, lalonde$education)

t.test(dw$re78, dw$age)
t.test(lalonde$re78, lalonde$age)
```

PSID and CPS Data
```{r}
require(Matching)
psid = read.dta("~/Downloads/psid_controls.dta")
summary(psid)

cps = read.dta("~/Downloads/cps_controls.dta")
summary(cps)
```

##Mahalanobis

```{r}
mahalanobis.match = Match(dw$re78, dw$treat, dw[c(2,3,4,5,6,7,8,9)])
```
```{r}
data(lalonde)
attach(lalonde)

#The covariates we want to match on
X = cbind(age, educ, black, hisp, married, nodegr, u74, u75, re75, re74)

#The covariates we want to obtain balance on
BalanceMat <- cbind(age, educ, black, hisp, married, nodegr, u74, u75, re75, re74,
                    I(re74*re75))

#
#Let's call GenMatch() to find the optimal weight to give each
#covariate in 'X' so as we have achieved balance on the covariates in
#'BalanceMat'. This is only an example so we want GenMatch to be quick
#so the population size has been set to be only 16 via the 'pop.size'
#option. This is *WAY* too small for actual problems.
#For details see http://sekhon.berkeley.edu/papers/MatchingJSS.pdf.
#
genout <- GenMatch(Tr=treat, X=X, BalanceMatrix=BalanceMat, estimand="ATE", M=1,
                   pop.size=16, max.generations=10, wait.generations=1)

#The outcome variable
Y=re78/1000

#
# Now that GenMatch() has found the optimal weights, let's estimate
# our causal effect of interest using those weights
#
mout <- Match(Y=Y, Tr=treat, X=X, estimand="ATE", Weight.matrix=genout)
summary(mout)

#                        
#Let's determine if balance has actually been obtained on the variables of interest
#                        
mb <- MatchBalance(treat~age +educ+black+ hisp+ married+ nodegr+ u74+ u75+
                   re75+ re74+ I(re74*re75),
                   match.out=mout, nboots=500)

# For more examples see: http://sekhon.berkeley.edu/matching/R.
[Package Matching version 4.9-2 Index]
```

