---
title: "Quantile Regression"
author: "Adrian Goedeckemeyer"
date: "10/10/2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Session 6.2

Use the raw Lalonde data set to experiment with quantile regression using Koenker’s ‘quantreg’ library in R. Then use one of your matched/balanced data sets, and obtain quantile estimates two ways: (a) quantreg; (b) by subtracting the same quantile (e.g., the median, or 0.5 quantile) of the matched control (Y0) distribution from the matched treatment (Y1) distribution. For each technique, produce a figure showing the quantile effects from quantiles 0.05 to 0.95. Compare the two sets of quantile estimates and assess their equivalence.

```{r}
require(Matching)
require(quantreg)
data(lalonde)
```

```{r}
attach(lalonde)
Y <- re78
X <- cbind(age, educ, black, hisp, married, nodegr, re74, re75, u74, u75)
BalanceMat <- X
Tr <- treat
gmout <- GenMatch(Tr=Tr, X=X, BalanceMat=BalanceMat, estimand="ATT", pop.size=100)
match <- Match(Y=Y, Tr=Tr, X=X, Weight.matrix=gmout, replace=FALSE)
mb <- MatchBalance(Tr ~ X, match.out=match, nboots=500)
qs <- 1:10/10
qs <- qs -.05
qr1 <- rq(Y ~ X, tau=qs)
plot(qr1)

qr2 <- rq(Y ~ X, data=lalonde[match$index.treated,], tau=qs)
```

