---
title: "Impact of Immigration on Extreme Right Vote"
author: "Adrian Goedeckemeyer"
date: "11/12/2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data Preparation

We combine the dataset from Arzheimers study (2009) with data on yearly immigration and percent of population that are foreign that were used in the replication by Javed and Gidron (2011). Parts of the data preparation are similar to their process

```{r}
require(foreign)

load('~/Downloads/nonimp.RData')
data <- x

##Center variables (done as according to the author).

salienzmean.c <- data$salienzmean - 3.84568
rvar.c <- data$rvar - 21.75423

##Load migration data.

mig.data <- read.csv("~/Downloads/migration.csv")

##Label migration data.

colnames(mig.data) <- c("year","migration","at","be","dk","fi","fr","deo","dew","gr","it","nl","no","pt","es","se","lu","sortcountry")

##Merge migration data with Arzheimer dataset by year and country.

new.data <- merge(data, mig.data, by=c("year","at","be","dk","fi","fr","deo","dew","gr","it","nl","no","pt","es","se","lu","sortcountry"))

##Load foreign population data.

fp.data <- read.csv("~/Downloads/foreign population.csv")

##Merge foreign population data with Arzheimer dataset by year and country.

new.data <- merge(new.data, fp.data, by=c("year", "sortcountry"))

##Create country dummies for merged dataset.

new.data$country <- factor(new.data$sortcountry, labels=c("AT", "BE","DE-E","DE-W","DK","ES","FI","FR","IT","LU","NL","NO","PT","SE"))

### Added check to verify that this works properly
sum(new.data$country[new.data$it==1]!="IT")==0
sum(new.data$country[new.data$deo==1]!="DE-E")==0

```

## Replicate Regression

As done by the Arzheimer paper, we are running a logistic regression, with the binary variable of extreme right vote as a dependent variable. We are copying their selection of covariates to test their model

```{r}
## We will test the model used in the paper by using a testset validation approach

set.seed(1)

train <- sample(1:nrow(new.data), nrow(new.data)*.8)
data.test <- new.data[-train,]

glm.fit <- glm(rexvote ~ male + age1 + age2 + age4 + mye1 + mye2 + farmerown + worker + retired + unemployed + zlrs + euschlecht + zsatisdmo + disp + lfed1 + migration + sur + migration:sur + replacementrate + sur:replacementrate + migration:replacementrate + rmax + salienzmean + rvar + rvar:salienzmean + country, family=binomial, data=new.data[train,])

summary(glm.fit)
coef(glm.fit)

## Test Model (we have to omit "LU" as it isn't included in the training set)
data.test <- na.omit(data.test)

glm.probs <- predict(glm.fit, type="response", newdata = data.test[data.test$country!="LU",])
glm.pred <- rep(0,nrow(data.test[data.test$country!="LU",]))
glm.pred[glm.probs >.1] <- 1

table(glm.pred, data.test$rexvote[data.test$country!="LU"])
mean(glm.pred[data.test$rexvote==0 || data.test$rexvote==1] == na.omit(data.test$rexvote[data.test$country!="LU"]))


## Refit with all data
glm.fit <- glm(rexvote ~ male + age1 + age2 + age4 + mye1 + mye2 + farmerown + worker + retired + unemployed + zlrs + euschlecht + zsatisdmo + disp + lfed1 + migration + sur + migration:sur + replacementrate + sur:replacementrate + migration:replacementrate + rmax + salienzmean + rvar + rvar:salienzmean + country, family=binomial, data=new.data)

```

## Look at Interaction effect between Immigration and Unemployemnt

We use the library *interplots* to replicate what was done in the original study in a more complicated simulation. This library fullfills the needs and returns us an illustration of the effects. In our model there is only a minimal interaction effect detectable.

```{r}
library(interplot)
par(mfrow=c(1,2))
interplot(m = glm.fit, var1 = "sur", var2 = "migration", hist = TRUE) +
  # Add labels for X and Y axes
    xlab("Migration Rate") +
    ylab("Unemployment Coef") +
  # Change the background
    theme_bw() +
  # Add the title
    ggtitle("Estimated Coefficient of Unemployment on Extreme Right Vote by Migration") +
    theme(plot.title = element_text(face="bold")) +
  # Add a horizontal line at y = 0
    geom_hline(yintercept = 0, linetype = "dashed") 

interplot(m = glm.fit, var1 = "migration", var2 = "sur", hist = TRUE) +
  # Add labels for X and Y axes
    xlab("Unemployment") +
    ylab("Migration Coef") +
  # Change the background
    theme_bw() +
  # Add the title
    ggtitle("Estimated Coefficient of Migration on Extreme Right Vote by Unemployment") +
    theme(plot.title = element_text(face="bold"))
par(mfrow=c(1,1))

```

## Simulation of increased Migration

Similar to what has been done by Arzheimer and Javed and Gidron we attempt to illustrate what happens if we keep all variables fixed and only increase the immigration variable from it's minimum to it's maximum. For all continuous variables we have chosen their mean, for variables with levels we choose the one connected to most likely ER vote, as these only determine the baseliine, but not the slope of the graph, due to no interactions with the migration variable.

The values picked by us predict a relatively high probability of voting for ER, but the impact of migration is almost linear and not especially strong.

```{r}

##Create means for all variables or set predetermined level.

means.mig <- c(0,1,0,0,1,0,0,0,0,1,-0.2823178,0.1254217,-0.09784655,4.614493,2.663593,0,8.295773,36.87453,5.586569,8.7076,16.40313,0)
names(means.mig) <- c("male","age1","age2","age4","mye1","mye2","farmerown","worker","retired","unemployed","zlrs","euschlecht","zsatisdmo","disp","lfed1","migration","sur","replacementrate","rmax","salienzmean","rvar","country")
means.mig$male = "nein"
means.mig$country = "IT"

##Simulate change in prob of ER vote due to change in net migration rate with all other variables held at mean.

mig <- seq(from = -4, to=16.3, by=.1)
ests.mig <- matrix(data=NA, ncol=length(mig) ,nrow=1)

for(j in 1:length(mig)){
  data.mig <- means.mig
	data.mig$migration <- mig[j] 
	ests.mig[j] <- predict(glm.fit, type="response", newdata = data.mig)
	}

plot(NA,NA, ylim= c(0.0,.25),xlim=c(-4,16.5), xlab="Net Migration Rate", ylab="Probability of Voting for the ER", main="The Effect of Net Migration on Voting for the ER", cex.main=1)
lines(mig, ests.mig)
abline(h=0)
```

We conclude that overall our results do not look to different from what Arzheimer and the previous replication have identified. Due to lack of familiarity with some libraries used by the original author(s), we did not simulate the variance as they have done and thus have less detailed results, but were able to extract the gist of their graphics. 

We want to now attempt a classification tree and random forest model to predict ER and compare predictive power as well as variable importance

## Classification Tree

```{r}
library(tree)
set.seed(2)

new.data2 <- na.omit(new.data)
rexfactor <- factor(new.data2$rexvote)

train <- sample(1:nrow(new.data2), nrow(new.data2)*.5)


tree.er <- tree(rexfactor ~ male + age1 + age2 + age4 + mye1 + mye2 + farmerown + worker + retired + unemployed + zlrs + euschlecht + zsatisdmo + disp + lfed1 + migration + sur + replacementrate + rmax + salienzmean + rvar + country,new.data2, subset = train, split = "gini")

plot(tree.er)
text(tree.er,pretty=0)

tree.pred = predict(tree.er, new.data2[-train,], type = "class")

table(tree.pred, rexfactor[-train])
mean(tree.pred == rexfactor[-train])

cv.er <- cv.tree(tree.er, FUN=prune.misclass, K = 20)

par(mfrow=c(1,2))
plot(cv.er$size,cv.er$dec,type = "b")
plot(cv.er$k,cv.er$dev,type="b")
cv.er

# Tree with 7 nodes performed best with lowest node number
prune.er=prune.misclass(tree.er,best=21)
par(mfrow=c(1,1))
plot(prune.er)
text(prune.er,pretty=0)

tree.pred=predict(prune.er,new.data2[-train,],type="class")
table(tree.pred, rexfactor[-train])
mean(tree.pred == rexfactor[-train])
```


## Random Forest Model

```{r}
library(randomForest)
rf.er = randomForest(rexfactor ~ male + age1 + age2 + age4 + mye1 + mye2 + farmerown + worker + retired + unemployed + zlrs + euschlecht + zsatisdmo + disp + lfed1 + migration + sur + migration:sur + replacementrate + rmax + salienzmean + rvar + country, data=new.data2, subset = train, importance =TRUE)
outcome.rf = predict(rf.er ,newdata=new.data2[-train,])
table(outcome.rf, rexfactor[-train])
mean(outcome.rf == rexfactor[-train])
importance(rf.er)
varImpPlot(rf.er)
```

# Part 2: Effect of Higher Education

After building regression models in which we saw that receiving university education lowers the logit score, we want to test if there is an actual effect of atending university on likelihood of voting for the extreme right. Towards this goal we will employ genetic matching. University education is the treatment variable and other personal as well as demographic data will be balanced on to estimate a treatment effect.

```{r}
library(Matching)

set.seed(2)
new.data2 <- na.omit(new.data)
new.data3 <- new.data2
Y <- new.data3$rexvote
Tr <- new.data3$mye2
male <- new.data3$male == "ja"

## Eliminate Variables that covary with university education such as: low education, left/right, dissatisfied with EU or Democracy

X <- cbind(male, new.data3$age1, new.data3$age2, new.data3$age4, new.data3$farmerown, new.data3$worker, new.data3$retired, new.data3$unemployed, new.data3$disp, new.data3$lfed1, new.data3$migration, new.data3$sur, new.data3$replacementrate, new.data3$rmax, new.data3$salienzmean, new.data3$at, new.data3$be, new.data3$deo, new.data3$dew, new.data3$dk, new.data3$es, new.data3$fi, new.data3$fr, new.data3$gr, new.data3$it, new.data3$nl, new.data3$no, new.data3$pt, new.data3$se)
colnames(X) <- c("male","age1","age2","age4","farmerown","worker","retired","unemployed","disp","lfed1","migration","sur","replacementrate","rmax","salienzmean","AT", "BE","DE-E","DE-W","DK","ES","FI","FR","GR","IT","NL","NO","PT","SE")

BalanceMat <- X

## Skipping GenMatch in knitted HTMl file, as it takes over an hour to complete and determines the ideal weights to be 1 for each variable under this caliper (we can do exact matching)
##gmout <- GenMatch(Tr=Tr, X=X, BalanceMat=BalanceMat, estimand="ATT", pop.size = 20, max.generations = 15, caliper = c(1,1,1,1,1,1,1,1,1,.5,.1,.1,.3,.01,.01,1,1,1,1,1,1,1,1,1,1,1,1,1,1), wait.generations = 3)

match <- Match(Y=Y, Tr=Tr, X=X, caliper = c(1,1,1,1,1,1,1,1,1,.5,.1,.1,.3,.01,.01,1,1,1,1,1,1,1,1,1,1,1,1,1,1))
summary(match)
mb <- MatchBalance(Tr ~ X, match.out=match, nboots=100)

par(mfrow = c(1,2))

plot(density(new.data3$salienzmean[Tr==0]), lwd = 3, col = "red", main = "Balance: Salience before Matching")
lines(density(new.data3$salienzmean[Tr==1]), lwd = 2, col = "blue")

plot(density(new.data3$salienzmean[match$index.control]), lwd = 3, col = "red", main = "Balance: Salience after Matching")
lines(density(new.data3$salienzmean[match$index.treated]), lwd = 2, col = "blue")

plot(density(new.data3$migration[Tr==0]), lwd = 3, col = "red", main = "Balance: Migration before Matching")
lines(density(new.data3$migration[Tr==1]), lwd = 2, col = "blue")

plot(density(new.data3$migration[match$index.control]), lwd = 3, col = "red", main = "Balance: Migration after Matching")
lines(density(new.data3$migration[match$index.treated]), lwd = 2, col = "blue")
# Sensitivity Analysis on these results
require(rbounds)
psens(match, Gamma = 2, GammaInc = 0.05)
```


